---
title: "AN588-Homework1-cshea26"
author: "Carly S McDermott"
date: "2025-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#Challenge 1
```{r}
library(stringr)
#This creates the vector from the line
v<- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."

#This removes punctuation
v <- gsub("[[:punct:]]","",v)

#Splitting string into individual words
v <- str_split(v, " ") [[1]]

#Extracting every third element from the vector (starting at the third element)
v <- v[seq(3, length(v), by = 3)]

v
```

#Challenge 2

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m

#I am extracting the 2nd, 3rd, and 6th columns and assigning them to the variable x
x <- m[, c(2, 3, 6 )]
x

#Assigning a new x value to the 6th to 8th rows and extracting them
x <- m[c(6, 8), ]
x

#This is another way to perform the task of assigning a new x value to elements from row 2, column 2 to row 6, column 9 
x <- m [2:6, 2:9]
x

```

#Challenge 3

```{r}
a <- array (data = 400:1, dim = c(5, 5, 4, 4))
a
#I am plugging in matrices to determine their values
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```

#Challenge 4

#Concatenating primate taxonomies together and organizing primate subgroups using the list function
```{r}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea,Tarsioidea)
names(Haplorhini) <- list("Anthropoidea","Tarsioidea")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Primates <- list(Haplorhini,Strepsirhini)
names(Primates) <- list("Haplorhini","Strepsirhini")
Primates
```

#Challenge 5
#Storing numbers as a 5 x 3 matrix labeled m3
#This matrix is filled by row
```{r}
m3 <- matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3

df <- as.data.frame(m3)
df[[2]] <- as.logical((df[[2]]))
df[[3]] <- as.factor((df[[3]]))
str(df)
```
#CHALLENGES
#CHALLENGE 1: I really struggled with understanding how to go about the first question for challenge one. I ended up using the str_split function to separate the sentence itself into different words but then struggled with how to extract every third word (starting at the 3rd word itself). Originally I tried doing [v <- str_split(v, " ") [[1]]] but that didn't do anything other than put the word "Stately" out. I ended up doing v <- v[seq(3, length(v), by = 3)] which worked for me. Still confused on whether or not I needed to remove punctuation but I think I overcame my issue.
#Challenge 4: When I tried to use the list function it didn't end up working. I realized then that I needed to use quotation marks when using the list function itself (which I didn't realize was different from actually concatenating the words together). I still feel like it looks kinda messy and would love any advice on how to make the output look cleaner.
#General challenge: I was looking at how to make my file prettier and kind of struggled with doing so aside from general # ## for making titles and subtitles; any advice? Thank you! 
