---
title: "AN588-Homework1-cshea26"
author: "Carly S McDermott"
date: "2025-01-28"
output: html_document
---
saadams// Above ^ is where you could change some of the design elements (like adding a theme or table of contents)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#Challenge 1
```{r}
library(stringr)
#This creates the vector from the line
v<- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."

#This removes punctuation
v <- gsub("[[:punct:]]","",v)

#Splitting string into individual words
v <- str_split(v, " ") [[1]]

#Extracting every third element from the vector (starting at the third element)
v <- v[seq(3, length(v), by = 3)]

v
```
saadams// line 16: I'm not sure if this is the correct process, but I might consider loading all of the packages you will be using at the very beginning of your document in a separate chunk.

saadams// 23-27: I personally put the split string in a different vector, I don't know if it matters which way it is done! This might be a more efficient way and I'm curious if this is what I should have done.

saadams// 27-29: I think it might be more concise to just do v[seq(3,length(v), by=3)] and get rid of line 29. I think just doing that would probably sequence and print the result you want and save you some space (it's not much space right now but maybe shortcuts are more helpful as this class gets harder)

#Challenge 2

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m

#I am extracting the 2nd, 3rd, and 6th columns and assigning them to the variable x
x <- m[, c(2, 3, 6 )]
x

#Assigning a new x value to the 6th to 8th rows and extracting them
x <- m[c(6, 8), ]
x

#This is another way to perform the task of assigning a new x value to elements from row 2, column 2 to row 6, column 9 
x <- m [2:6, 2:9]
x

```
saadams// 48: You could have written this line x <- m[6:8,] if you wanted to do it the same as you how you did line 52. I realized writing this though that I did the same thing in my code. I don't think it's wrong for us to do both but it might be more consistent to choose one way

#Challenge 3

```{r}
a <- array (data = 400:1, dim = c(5, 5, 4, 4))
a
#I am plugging in matrices to determine their values
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```
saadams// 61: I might comment what the line does in case you look back on this later but this is all pretty much what I did. I think you were more concise with your comments than I was.

#Challenge 4

#Concatenating primate taxonomies together and organizing primate subgroups using the list function
```{r}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea,Tarsioidea)
names(Haplorhini) <- list("Anthropoidea","Tarsioidea")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Primates <- list(Haplorhini,Strepsirhini)
names(Primates) <- list("Haplorhini","Strepsirhini")
Primates
```
saadams// we did pretty much everything the same thing! I added some spaces between the different groupings to make it a little easier to keep track of what I was doing.

#Challenge 5
#Storing numbers as a 5 x 3 matrix labeled m3
#This matrix is filled by row
```{r}
m3 <- matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3

df <- as.data.frame(m3)
df[[2]] <- as.logical((df[[2]]))
df[[3]] <- as.factor((df[[3]]))
str(df)
```
saadams// we pretty much did the same thing! Your coding made me realize I should use <- for my version of line 96 instead of =.

#CHALLENGES
#CHALLENGE 1: I really struggled with understanding how to go about the first question for challenge one. I ended up using the str_split function to separate the sentence itself into different words but then struggled with how to extract every third word (starting at the 3rd word itself). Originally I tried doing [v <- str_split(v, " ") [[1]]] but that didn't do anything other than put the word "Stately" out. I ended up doing v <- v[seq(3, length(v), by = 3)] which worked for me. Still confused on whether or not I needed to remove punctuation but I think I overcame my issue.
#Challenge 4: When I tried to use the list function it didn't end up working. I realized then that I needed to use quotation marks when using the list function itself (which I didn't realize was different from actually concatenating the words together). I still feel like it looks kinda messy and would love any advice on how to make the output look cleaner.
saadams// I also was wanting to make mine look better. Mine looks very similar to yours honestly. The only difference is that I left a space between the different levels I coded for just so it was easier for me to track which species belonged to group.

#General challenge: I was looking at how to make my file prettier and kind of struggled with doing so aside from general # ## for making titles and subtitles; any advice? Thank you! 
saadams// So I played around with mine a little and honestly am overwhelmed by all of the options. I worked in a quarto document (which should be similar to R Markdown I think), but I also added a theme, a code block border to make the code blocks stand out when rendered, and a table of contents. The table of contents was actually really helpful for keeping track of the things I was doing. You can edit all of this in the YAML (which is just the first block of code you did in lines 1-6)

# Peer Commentaary

### 1) What you learned from running their Original Homework Code that helped improve your own code.
I was trying to figure out what lines 8-10 were accomplishing. I'm not sure if it would be helpful to have or not in my quarto document because it seems like my document automatically displays the code when it's run.

In Challenge 3, I think Carly was more concise with her commenting. For example, in my code I commented after every subset of the array I made. This wasn't really necessary and could easily become redundant.

### 2) What you did in your own code that might help to improve theirs.
For Challenge 1, I named the items I was working with pretty specifically (ex. Ulysses_vector) and also worked with different vectors instead of updating the changes (original, split) to the same vector. I'm honestly not sure if either is better or if they are both equally acceptable ways.


### 3) What challenges, if any, you both faced in your code that could not be helped by comparison.
I realized in Challenge 2 that both of us were not using the same method to select rows/columns every time. I don't think it has to be the same, but it does seem like the code might read better if we do so I'll probably change mine to reflect this too.

### 4) Whether the annotation/commenting on your peer’s Original Homework Code is readable and interpretable to you, and if not then how it could be improved.
Overall Carly's code was very readable! I think she overall did a good job commenting on her code, but should maybe add another comment here or there if she thinks it would be difficult to remember how to do certain things a few weeks or months from now. I think Challenge 4 is a little hard to read, but I struggled with the same thing and was hoping to get some advice during class about how to construct this challenge to be more organized.
